---
title: "My Favorite Thing in R"
---

```{r setup, include = F}
knitr::opts_chunk$set(fig.path = "../images/")
```
My programming skills in R are continuing to improve over time. There are many things I have grown like about R, but the visualization tools have to be my favorite. 

The `ggplot2` package is quite intuitive once you get used to it, as is the entire `tidyverse`. There are plenty of beautiful figures you can make, and I love the coloring mechanism within this package that allows for simple coloring based on a variable. One of my favorite type of plots to make is a stacked histogram and density plot, colored by a categorical variable.

There is another package that I am extremely fond of as well, which is `corrplot`. Often times, it is hard to grasp a lot of information from staring at a correlation matrix full of numbers. This package makes that fun! Let me show you.

All you need to do is create the correlation matrix as is, and then plug that into the `corrplot` function!

```{r, eval = T}
library(corrplot)
cor <- cor(mtcars)
corrplot(cor)
```

If you don't like the circles, don't fret! You can use squares too. You can also order the variables based on the angular order of the eigenvectors, which I think makes the plot look a lot nicer. 

```{r, eval = T}
corrplot(cor, method = "square", order = "AOE")
```

I hope this convinced you to use the `corrplot` package in your next project!

